\documentclass[12pt]{article}

  \usepackage[english]{babel}
  \usepackage{hyperref}
  \usepackage{fancyhdr}
  \usepackage[dvipsnames]{xcolor}
  \usepackage{listings}
  \usepackage{parcolumns}
  \usepackage{algorithm}
  \usepackage{algorithmicx}
  \usepackage{algpseudocode}
  \usepackage{enumitem}
  \usepackage{geometry}
  \usepackage{soul}
  \usepackage{graphicx}
  \usepackage{enumitem}
  \usepackage{csquotes}
  \usepackage{bookmark}
  \usepackage{mdframed}
  \usepackage{mathtools}
  \usepackage{amsmath}
  \usepackage{amsthm}
  \usepackage[toc]{appendix}
  \usepackage[
    backend=biber,%
    style=apa%
  ]{biblatex}

  % Bibliography Setup
  \addbibresource{main.bib}
  \newcommand{\CiteSection}[2]{%
    (\autocite{#1}, ~\S {#1})
  }

  % Theorem Environments
  \theoremstyle{definition}
  \newtheorem*{defn*}{Definition}
  \theoremstyle{plain}
  \newtheorem*{equ*}{Equation}

  % Definitions for Algorithmic Environments
  \algdef{SE}[VARIABLES]{GVariables}{EndGVariables}
    {\algorithmicvariables}
    {\algorithmicend\ \algorithmicvariables}
  \algnewcommand{\algorithmicvariables}{\textbf{global variables}}
  
  \algdef{SE}[VARIABLES]{LVariables}{EndLVariables}
    {\algorithmiclvariables}
    {\algorithmicend\ \algorithmiclvariables}
  \algnewcommand{\algorithmiclvariables}{\textit{local variables}}

  \renewcommand{\algorithmicrequire}{\textbf{Input:}}
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \renewcommand\thealgorithm{}

  % Settings for math-mode
  \makeatletter
  \def\mathcolor#1#{\@mathcolor{#1}}
  \def\@mathcolor#1#2#3{%
    \protect\leavevmode
    \begingroup
      \color#1{#2}#3%
    \endgroup
  }
  \makeatother


  % Image Directory
  \graphicspath{ {screenshots/} }
  % Hyperlink Setup
  \hypersetup{
    colorlinks = true,
    urlcolor = blue,
    linkcolor = blue,
    citecolor = blue
  }
  % Page and Text Layout
  \pagestyle{fancy}
  \geometry{%
    a4paper,%
    top=15pt,%
    bottom=1in,%
    left=1in,%
    right=1in%
  }
  \setlength{\headheight}{15pt}

  \newenvironment{ldefinitions}
    {\left.\begin{aligned}}
    {\end{aligned}\right\rbrace}

  \title{%
    Module 1 Discussion 1%
    \large{Myths and Mythology}
  }
  \author{Ashton Hellwig}
  \date{\today}
  \rhead{HUM115 Module 1 Discussion 1}

\begin{document}
  \maketitle
  \tableofcontents
  \newpage


  \part{Initial Post}

    \section{Discussion Prompt}
      \begin{mdframed}
        \subsection{Overview}
          In this discussion we will examine what your belief of what a myth is
            and what purpose(s) it has.  You will need to read the Preface and
            Introduction to our textbook, (pgs. xi-xxi,) as a means to respond
            to this discussion.

        \subsection{Instructions}
          Compose a brief statement that clarifies your belief of what myth is
            and what purpose(s) it has. Give an example of some legend or tale
            from your experience and explain how the elements of that tale
            reinforced (or were intended to reinforce) particular customs or
            values. Please try to limit your contribution to an example that
            seems to have a purpose. Local ghost stories and/or odd strange
            events usually do not qualify. Compare your insights with at least
            two classmates.

          Be sure to proof-read your work (ALL rules of grammar, punctuation,
            spelling apply) and remember that I expect two well constructed
            paragraphs. I WILL deduct points for quick and shoddily written
            posts.
      \end{mdframed}

    \section{Initial Post}
      \subsection{Myths: Purpose and Meaning}
        A myth to me is similar to folklore in that both categories tend to be
          orally passed-down to younger family members via their elders
          \autocite[p.~xiii]{textbook}. The difference between folklore and
          myths is in the plot and theme. Folklore tends to have some sort of
          main character which needs to overcome an obstacle and the story
          follows them. Myths tend to be more religious and/or spiritual in
          motivation -- such as ``\textit{The Flood Myth}''
          \autocite[p.~xiv]{textbook}. This is due to the fact that myths are
          most commonly used to explain \textit{``big-picture''}-type
          questions in human nature and history.

        I am currently finding it difficult to think of a myth which has had
          impact on my life \textit{personally}. This is most likely due to
          always, even as a child, I have focused on trying to have a more
          analytical view of most things (especially things which are hard
          to explain in natural terms). After reading some other experiences
          from classmates perhaps I will be reminded of something which happened
          while far younger that I am unable to now.


  \newpage
  \part{Responses}

    \section{Response 1}
      \begin{mdframed}
        Reply to \textbf{Hayley Salazar-Gibson} (\textit{Post ID: 38582055})
      \end{mdframed}
      \begin{quote}
          I believe that Myths are a huge part of different generations.
            They are stories that have been passed down for centuries. A
            lot of people live by these myths, because that Is what they were
            taught spiritually. That is why I think they hold such a huge
            impact on certain people, nd the stories continue to do be passed
            on.
            
          One of the myths that I remember the most was the La Llorona.
            I believe that this myth is one story that everyone knows! Its very
            common. I remember this one story the most, because my auntie donna
            told us this myth when we were camping. It stuck with me for years
            when I was little, because it scared me to death! I remember her
            mostly saying that this lady drowned her two babies in a river, and
            then later killed herself. She now searches for her boys along side
            the river. Also that if you listened very closely, you could hear
            her weeping for her sons. My Aunt later said that if we didn't
            behave that the La Llorona would come find us and take us back to
            the river with her. What made it even worse, our campsite was next to
            a river!

          Now you can see why, till this day at 21 years old I still get the
            creeps when it comes to camping or staying in a house near the
            river!! 
      \end{quote}
      I have heard the La Llorona myth before! My girlfriend explained it to me
        a while back. I was horrified! I could not fathom that this is a story
        that is meant to be told to \textit{children}, but I suppose for children
        this is a strong motivator to prevent any misbehavior.
      
      I am having trouble trying to distinguish the difference between a
        \textit{myth} and \textit{folklore}. I had seen some sources
        describe myths as dealing with broad, overarching life questions
        or explaining natural phenomenon (usually with the use of Gods or
        Goddesses) while folklore is more stories passed down through the
        generations \autocite{lombardi_2020}. What are your thoughts on this?


    \section{Response 2}
      \begin{mdframed}
        Reply to \textbf{} (\textit{Post ID: }) 
      \end{mdframed}
      \begin{quote}
        Placeholder for Response \#2.
      \end{quote}
      Placeholder.

  % Bibliography
  \newpage
  \nocite{textbook}
  \printbibliography[
    heading=bibintoc,
    title={Works Cited}
  ]
\end{document}
